### 2009-11-19 doc/manuals/janitor/tex_installation/installation.tex
Review, reformatting.

\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for Janitor.}{Log4perl is used for the internal logging of Janitor, while the 
                   Redland RDF library is used for accessing the knowledge base of Runtime Environments.}
        \label{tab:install_dependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for Janitor.}{The library libperl-dev provides header files which are needed to link the 
                   WebService to the Perl interpreter.}
        \label{tab:install_dependencies_optional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

The Janitor will be installed by default along with ARC1. Support for
the dynamic REs can be completely disabled at compile time by using
the \textit{configure} flags \textit{--disable-janitor-service} for
the complete janitor or \textit{--disable-janitor-webservice} to only
disable the Janitor's Web Service.

@@

The parameter \texttt{enable} specifies whether the Janitor shall be used within A-REX or not. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective the user and group id shall be used for Janitor. 
The \texttt{registrationdir} describes the directory in which the subdirectories \texttt{jobs} and \texttt{rtes} will be created.
In these directories the states of the jobs and the runtime environments will be stored. 
The knowledge base of installable packages is specified by the parameter \texttt{catalog}. 
Its value can be any kind of URL pointing to a file written in the Resource Description Framework (RDF) format.
The specification of the RDF file will be explained in detail in section~\ref{sec:catalog}.
The parameter \texttt{downloaddir} assigns the directory in which the installation files will be saved after they have been 
downloaded or copied from the repository which was specified by the catalog. The \texttt{installationdir} finally specifies the
directory into which all packages will be installed and should be 
available for all computing elements, i.e.\ by using a shared volume.
If the configuration file furthermore contains the \texttt{runtimedir} tag within the section \texttt{grid-manager}, the Janitor will also
create a symbolic link in the \texttt{runtimedir} pointing to the configuration script of the installation done by the Janitor.
The tags \texttt{jobexpirytime} and \texttt{rteexpirytime} are used for automated cleanup and is defined in seconds.
The default value for the \texttt{jobexpirytime} is seven days and for the \texttt{rteexpirytime} three days. 
The additional tags \texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and \texttt{deny\_rte} are used to include
or exclude certain base packages or runtime environments of the catalog. This feature is useful, if the catalog is maintained by
a higher organization.
The path to the log4perl configuration file is defined by the tag \texttt{logconf}.
An example how to configure ARC and log4perl is provided in the Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

@@

The Janitor is designed for the usage on Linux distributions.
Its porting to other platforms has not yet been addressed.

>>>>

\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for Janitor.}{Log4perl is used for the internal logging of Janitor, while the 
                   Redland RDF library is used for accessing the catalogue of Runtime Environments.}
        \label{tab:install_dependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for the Janitor.}{The library libperl-dev provides the required header files to link the 
                   WebService to the Perl interpreter.}
        \label{tab:install_dependencies_optional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

The Janitor will be installed by default along with ARC-NOX. Support for
the dynamic REs can be completely disabled at compile time by using
the \textit{configure} flags \textit{--disable-janitor-service} for
the complete janitor or \textit{--disable-janitor-webservice} to only
disable the Janitor's Web Service.

@@

The parameter \texttt{enable} specifies whether the Janitor shall be used
within A-REX or not. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.\footnote{For
the time speaking, you need to have started the ARC services as root to
allow the Janitor to change into those IDs.} The \texttt{registrationdir}
describes the directory in which the subdirectories \texttt{jobs} and
\texttt{rtes} will be created.  In these directories the states of the
jobs and the runtime environments will be stored.  The knowledge base
of installable packages is specified by the parameter \texttt{catalog}.
Its value can be any kind of URL pointing to a file written in the
Resource Description Framework (RDF) format.  The specification of the
RDF file will be explained in detail in section~\ref{sec:catalog}.
The parameter \texttt{downloaddir} assigns the directory in which
the installation files will be saved after they have been downloaded
or copied from the repository which was specified by the catalog. The
\texttt{installationdir} finally specifies the directory into which all
packages will be installed and should be available for all computing
elements, i.e.\ by using a shared volume.  If the configuration file
furthermore contains the \texttt{runtimedir} tag within the section
\texttt{grid-manager}, the Janitor will also create a symbolic link
in the \texttt{runtimedir} pointing to the configuration script of the
installation performed by the Janitor.  The tags \texttt{jobexpirytime}
and \texttt{rteexpirytime} are used for an automated cleanup and is
defined in seconds.  The default value for the \texttt{jobexpirytime} is
seven days and for the \texttt{rteexpirytime} three days.  The additional
tags \texttt{allow\_base} \texttt{deny\_base} \texttt{allow\_rte} and
\texttt{deny\_rte} are used to include or exclude certain base packages
or runtime environments of the catalog. This feature is useful, if
the catalog is maintained by a higher organization.  The path to the
log4perl configuration file is defined by the tag \texttt{logconf}.
An example how to configure ARC and log4perl is provided in the
Listings~\ref{lst:arc_conf} and ~\ref{lst:log_conf}.

@@

The Janitor is designed to be used on Linux distributions.
Its porting to other platforms has not yet been addressed.
